Ion pairing controls rheological properties of ``processionary'' polyelectrolyte hydrogels

### 2016-07-12 PALSE/talk_Kyoto.tex
solubility in a row embed chemfig in a named tikzpicture
polyelectrolytes physics -> can we measure B from rheology?

% Allow the usage of graphics (.jpg, .png, etc.) in the document
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{arrows,shapes,backgrounds, calc, positioning, topaths,chains, intersections, decorations.markings, decorations.text, shapes.geometric, matrix,patterns,mindmap}
%\usetikzlibrary{positioning, patterns,topaths,chains,matrix}

@@

\begin{frame}{Counterion condensation}
	\tikzsetnextfilename{solubility}%
	\input{fig_presentation/solubility.pgf}
	\begin{itemize}
		\item Too much condensation prevents dissolution
		\item<2-> Direct Hoffmeister series $\ce{I-}<\ce{Br-}<\ce{Cl-}<\ce{F-}$
		\item<3> \ce{\pi+-\pi+} interactions {\tiny\setatomsep{1.5em}$\raisebox{-0.5em}{\chemfig{[2]*5(--N(-)---)}}<\raisebox{-0.5em}{\chemfig{[2]*5(-N(-)-=N-=)}}$}
		\item<3> \ce{PIm+Br-} < \ce{PIm+I-} < \ce{PPyr+Cl-} < \ce{PPyr+Br-} < \ce{PPyr+I-}
	\end{itemize}
\end{frame}

>>>>

% Allow the usage of graphics (.jpg, .png, etc.) in the document
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{arrows,shapes,backgrounds, calc, positioning, topaths,chains, intersections, decorations.markings, decorations.text, shapes.geometric, matrix,patterns,mindmap,fit}
%\usetikzlibrary{positioning, patterns,topaths,chains,matrix}

@@

\begin{frame}<1>[label=condensationranking]{Counterion condensation}
	\tikzsetnextfilename{solubility}%
	\input{fig_presentation/solubility.pgf}
	\begin{itemize}
		\item Too much condensation prevents dissolution
		\begin{itemize}
			\item water poor solvent for polymer backbone
			\item polyelectrolytes solubilized by electrostatic repulsion
		\end{itemize}
		\item<2-> Direct Hoffmeister series $\ce{I-}\alert{<}\ce{Br-}\alert{<}\ce{Cl-}\alert{<}\ce{F-}$\\
	\hfill\textit{\scriptsize Hofmeister 1888; Zhang Annu Rev Phys Chem 2010; Schwierz Langmuir 2010}
		\item<3-> \ce{\pi+-\pi+} interactions trap counterions\raisebox{-0.5em}{%
			\begin{tikzpicture}[every node/.style={inner ysep=0,font=\tiny\setatomsep{1.5em}}]
			\node[left=0.5em] (Pyr){\chemfig{[0]*5(--N(-)---)}};
			\node[right=0.5em] (Im){\chemfig{[2]*5(-N(-)-=N-=)}};
			\node[font=\normalsize]{$\alert{<}$};
			\end{tikzpicture}}\\
			\hfill\textit{\scriptsize
			Geronimo PCCP 2011;
			Matthews PCCP 2014;
			Gao J Mol Graph Model 2015}
	\end{itemize}
\end{frame}

\begin{frame}{Condensation and solubility}
	\begin{itemize}
		\item All counterions condensed $\Rightarrow$ neutral $\Rightarrow$ not soluble
	\end{itemize}
	\tikzsetnextfilename{polyelectrolytes_condensed}%
	\input{fig_presentation/polyelectrolytes_condensed.pgf}
	\begin{itemize}
		\item ``Enough'' free counterions $\Rightarrow$ repulsion $\Rightarrow$ soluble
	\end{itemize}
	\tikzsetnextfilename{polyelectrolytes}%
	\input{fig_presentation/polyelectrolytes.pgf}
\end{frame}

\againframe<2-3>{condensationranking}

\begin{frame}{\# chains between cross links}%
\tikzsetnextfilename{frequency}%
\input{fig_presentation/frequency.pgf}
\begin{itemize}
\item Procession length increases with counterion condensation
\end{itemize}
\end{frame}

\begin{frame}{Polyelectrolytes physics}
	\structure{Can we measure counterion condensation from rheology?}

	\begin{itemize}
		\item 1 dissociated counterion every \alert{$A$} monomers
		\begin{itemize}\item large $A$, more condensed\end{itemize}
		\item poor solvent: reduced temperature $\alert{\tau} = 1 -T/\Theta$
		\begin{itemize}\item \ce{PIm+F-} non soluble at \SI{100}{\celsius} $\Rightarrow\tau>0.2$ \end{itemize}
		\smallskip
		\item extension parameter $\alert{B} = \frac{\text{extended length}}{\text{diameter}}$ of electrostatic blob
		\smallskip
		\item from scaling theory: $B \sim A^{4/3} \tau$\hfill \textit{\scriptsize Rubinstein Macromol. 1996}
	\end{itemize}

	\tikzsetnextfilename{scales}%
	\input{fig_presentation/scales.pgf}
	\begin{center}
	\structure{Can we measure $B$ from rheology?}
	\end{center}
\end{frame}
